Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report

### 2024-06-07 paper.qmd
Code for new combined effects plots. Improved coefficient plot. Used dietary weights for one immune model.

```{r}
#| label: fig-coefs
#| fig-width: 10
#| fig-height: 8
#| fig-cap: Coefficients of sex-specific strength, and strength X sex interaction for our four mating success outcomes and our five sets of potential confounding variables. Partnered coefficients are from logistic regressions, partner number coefficients are from quasi-Poisson glm regressions, and age at first sex coefficients are from Gaussian glm regressions. Bars are 95\% CIs. Left: Pilot study results. Right: Confirmatory study results. For the full regression tables, see the SI.

@@

:::{#fig-stage2effects}
```{r}
effects_plots(models_stage2)
```

>>>>

```{r}
#| label: fig-coefs
#| fig-width: 10
#| fig-height: 8
#| fig-cap: "Coefficients of sex-specific strength, and strength X sex interaction for our four mating success outcomes and our five sets of potential confounding variables. Partnered coefficients are from logistic regressions, partner number coefficients are from quasi-Poisson glm regressions, and age at first sex coefficients are from Gaussian glm regressions. Bars are 95\% CIs. Left: Pilot study results. Right: Confirmatory study results. For the full regression tables, see the SI."

@@

:::{#fig-stage2effects}
```{r}
plot_effects_all
```
